---
title: "Lobster Predator Indices"
author: "Adam A. Kemberling"
date: "Updated on: `r Sys.Date()`"
output: 
  html_document:
    toc: TRUE
    toc_float:
        collapsed: FALSE
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, 
                      message = F, 
                      warning = F, 
                      comment = "", 
                      fig.align = "center", 
                      fig.height = 6, 
                      fig.width = 6)

####  Packages  ####
library(sf)
library(tidyverse)
library(targets)
library(gmRi)
library(scales)

# paths
box_paths <- research_access_paths()
res_path <- box_paths$res

# Mapping polygons
new_england <- rnaturalearth::ne_states("united states of america", returnclass = "sf")
canada <- rnaturalearth::ne_states("canada", returnclass = "sf") 

# Set ggplot theme for figures
theme_set(theme_bw())

# Set theme up for maps
map_theme <- list(
  theme(
    panel.border       = element_rect(color = "black", fill = "transparent"),
    plot.background    = element_rect(color = "transparent", fill = "transparent"),
    line               = element_blank(),
    axis.title.x       = element_blank(), # turn off titles
    axis.title.y       = element_blank(),
    legend.position    = "bottom", 
    legend.title.align = 0.5)) 
```


`r use_gmri_style_rmd(css_file = "gmri_rmarkdown.css")`

# Lobster Predator Indices

The idea behind the lobster predator index is to use characteristics of the fish community that prey on lobster as a biological indicator for predicting patterns in lobster abundance/biomass/recruitment.


## Data Prep

The predator data used is sourced from the northeast trawl survey, conducted by the Northeast Fisheries Science Center. This survey runs every spring and fall sampling the seafloor using trawling gear towed behind a research vessel. Data from the survey includes abundance and size information for fishes found on the Northeastern US shelf.


### Trawl Survey Data Prep

Data from the survey is loaded for abundance-based analyses, with some filtering done to remove stratum that are sampled less-frequently following a survey design change in 2008. Following the standard tidy-up steps, each species then has their expected length-weight biomasses estimated using published growth curve equations.

```{r}
# Load clean trawl data, add length weight data
nefsc_clean <- gmRi::gmri_survdat_prep(survdat_source = "most recent")
nefsc_clean <- add_lw_info(nefsc_clean, cutoff = TRUE)
```


### Subsetting Data to the Gulf of Maine

For the predator indices we are narrowing our attention to patterns within the Gulf of Maine. This is done to relate these patterns in predators to lobster observations in the area. These include regional landings, juvenile surveys, and recruitment indices. To do this data is only kept if it is sampled from within trawl stratum that  we typically associate with the Gulf of Maine

**Loading Trawl Survey Strata:**

```{r}
# Load the strata
survey_strata <- read_sf(str_c(res_path, "Shapefiles/BottomTrawlStrata/BTS_Strata.shp"))  %>% 
  janitor::clean_names() %>% 
  filter(strata >= 01010 ,
         strata <= 01760,
         strata != 1310,
         strata != 1320,
         strata != 1330,
         strata != 1350,
         strata != 1410,
         strata != 1420,
         strata != 1490) 


# Key to which strata = which regions
strata_key <- list(
  "Georges Bank"          = as.character(13:23),
  "Gulf of Maine"         = as.character(24:40),
  "Southern New England"  = str_pad(as.character(1:12), width = 2, pad = "0", side = "left"),
  "Mid-Atlantic Bight"    = as.character(61:76))

# Assign Areas by Strata
survey_strata <- survey_strata %>% 
  mutate(
    strata = str_pad(strata, width = 5, pad = "0", side = "left"),
    strata_num = str_sub(strata, 3, 4),
    area = case_when(
      strata_num %in% strata_key$`Georges Bank` ~ "Georges Bank",
      strata_num %in% strata_key$`Gulf of Maine` ~ "Gulf of Maine",
      strata_num %in% strata_key$`Southern New England` ~ "Southern New England",
      strata_num %in% strata_key$`Mid-Atlantic Bight` ~ "Mid-Atlantic Bight",
    TRUE ~ "Outside Major Study Areas")) %>% 
  select(finstr_id, strata, strata_num, area, a2, str2, set, stratuma, str3, geometry)
```

**Mapping the Trawl Regions:**

```{r}
# Map it against the coastline
ggplot() +
  geom_sf(data = new_england, size = 0.3) +
  geom_sf(data = canada, size = 0.3) +
  geom_sf(data = survey_strata, aes(fill = area)) +
  coord_sf(xlim = c(-77, -64.5), ylim = c(34.4, 45.75), expand = FALSE) +
  guides(fill = guide_legend(nrow = 2)) +
  theme_bw() +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  map_theme +
  labs(subtitle = "Trawl Survey Regions")

```

**Subset to Gulf of Maine:**

```{r}
nefsc_gom <- nefsc_clean %>% 
  filter(survey_area == "GoM")
```


### Assigning Lobster Strata

Unfortunately the trawl survey and the surveys for lobster abundances are done using a different area stratification. To perform a more direct comparison among areas we reassign the trawl stations based on where they fall within the lobster survey strata.

#### Loading Strata

```{r}
# Lobster Strata
lobstrata <- read_sf(paste0(res_path, "Shapefiles/Statistical_Areas/Statistical_Areas_2010_withNames.shp"))
lobstrata <- rename_all(lobstrata, tolower)

# Subset the ones in GOM to plot faster
lobstrata_gom <- filter(lobstrata, id %in% c(464:467, 511:515, 521, 522, 526, 551, 561))


# Map against the Coast
ggplot() +
  geom_sf(data = new_england, size = 0.3) +
  geom_sf(data = canada, size = 0.3) +
  geom_sf(data = lobstrata_gom, fill = "transparent", show.legend = FALSE) +
  coord_sf(xlim = c(-71.5, -64.5), ylim = c(41.5, 45.75), expand = FALSE) +
  map_theme +
  theme(legend.position = "bottom", legend.title = element_blank()) +
  labs(subtitle = "Lobster Strata in the Gulf of Maine")
```

#### Strata Re-assignment

The reassignment is done by overlaying the starting locations for the trawl stations with the survey strata. Each station is assigned based on which strata is falls within. From there we can estimated area-weighted catch rates within each of them.

**Strata Re-assignment function:**

```{r}
# Assign statistical zone from new sf for stat zones
assign_stat_zones <- function(survdat, zone_sf, strata_col_in = "id", strata_col_out = "stat_zone", keep_NA = FALSE){
  
  # Transfer to shorthand names
  x <- as.data.frame(survdat)
  out_name_sym <- sym(strata_col_out)
  
  # use only station data for overlay/intersection
  stations <- distinct(x, cruise6, stratum, station, decdeg_beglat, decdeg_beglon)
  
  # Convert stations to sf
  stations_sf <- st_as_sf(stations, coords = c("decdeg_beglon", "decdeg_beglat"), crs = 4326, remove = FALSE)
  
  # Project to Lambert Conformal Conic
  lcc <- st_crs("+proj=lcc +lat_1=20 +lat_2=60 +lat_0=40 +lon_0=-72 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0 ") 
  stations_sf <- st_transform(stations_sf, crs = lcc)
  
  # Prepare statistical zones in same CRS
  stratum <- st_transform(lobstrata, crs = lcc)
  
  # rename stratum column to match desired label
  names(stratum)[which(names(stratum) == strata_col_in)] <- strata_col_out
  
  # Identify points within each polygon/strata
  stations_sf <- st_join(stations_sf, stratum, join = st_within, left = TRUE)
  
  # Don't need to convert back b/c we kept coordinates
  stations_wgs <- st_drop_geometry(stations_sf)
  
  # Keep NA's or not?
  if(keep_NA == F){ stations_wgs <- filter(stations_wgs, is.na({{out_name_sym}}) == FALSE)}
  
  # Join station assignments back into full data
  out <- right_join(stations_wgs, x, by = c('cruise6', 'stratum', 'station', "decdeg_beglat", "decdeg_beglon")) %>% 
    mutate({{out_name_sym}} := as.character({{out_name_sym}}))

  # return the table
  return(out)
  
  }

```

**Assigning Lobster Strata:**

```{r}
# Assign those zones!
nefsc_lobsta_zones <- assign_stat_zones(survdat = nefsc_gom, 
                                        zone_sf = select(lobstrata, id, short_name, geometry), 
                                        strata_col_in = "id", 
                                        strata_col_out = "lobster_strata",
                                        keep_NA = FALSE)
```

**Validate by Mapping:**

```{r}
# make sf to check
gom_dat_sf <- nefsc_lobsta_zones %>% 
  distinct(decdeg_beglon, decdeg_beglat, lobster_strata) %>% 
  st_as_sf(coords = c("decdeg_beglon", "decdeg_beglat"), crs = 4326) 

# map check
ggplot() +
  geom_sf(data = gom_dat_sf, aes(color = lobster_strata)) +
  geom_sf(data = lobstrata, fill = "transparent") +
  geom_sf(data = new_england, size = 0.3) +
  geom_sf(data = canada, size = 0.3) +
  coord_sf(xlim = c(-71, -65.8), ylim = c(41, 44.5)) +
  map_theme +
  theme(legend.position = "bottom") + 
  guides(color = guide_legend("Lobster Strata", title.position = "top", title.hjust = 0.5))
```

**Drop Strata with Incomplete Representation:**


```{r}
gom_dat <- nefsc_lobsta_zones %>% 
  filter(survey_area == "GoM",
         lobster_strata %not in% c(561, 522, 551, 526, 466, 467),
         is.na(lobster_strata) == FALSE)
```

**Validate by Mapping:**

```{r}
# make sf to check
gom_dat_sf_2 <- gom_dat %>% 
  distinct(decdeg_beglon, decdeg_beglat, lobster_strata) %>% 
  st_as_sf(coords = c("decdeg_beglon", "decdeg_beglat"), crs = 4326) 

# map check
ggplot() +
  geom_sf(data = gom_dat_sf_2, aes(color = lobster_strata)) +
  geom_sf(data = lobstrata, fill = "transparent") +
  geom_sf(data = new_england, size = 0.3) +
  geom_sf(data = canada, size = 0.3) +
  coord_sf(xlim = c(-71, -65.8), ylim = c(41, 44.5)) +
  map_theme +
  theme(legend.position = "bottom") + 
  guides(color = guide_legend("Lobster Strata", title.position = "top", title.hjust = 0.5))
```


### Calculate the Areas of Strata

To weight the catch rates of each stratum against one-another, they are weighted using their interior areas in square kilometers.

```{r}
#### Get Stratum Area in km2  ####

# Lambert Conformal Conic
lcc <- st_crs("+proj=lcc +lat_1=20 +lat_2=60 +lat_0=40 +lon_0=-72 +x_0=0 +y_0=0 +datum=NAD83 +units=m +no_defs +ellps=GRS80 +towgs84=0,0,0 ")
lobstrata_lcc <- st_transform(lobstrata, lcc)

# Get areas
# rename the id column to match nefsc_lobsta
# drop geometry
zone_areas <- lobstrata_lcc %>% 
  rename(lobster_strata = id) %>% 
  mutate(lobster_strata = as.character(lobster_strata),
         area_m2 = st_area(lobstrata_lcc),
         area_km2 = units::set_units(area_m2, "km^2"),
         area_km2 = as.numeric(area_km2)) %>% 
  select(lobster_strata, area_km2) %>% 
  st_drop_geometry()


# merge in the areas
gom_weights <- left_join(gom_dat, zone_areas, by = "lobster_strata")


# Bar plot for area of each
gom_weights %>% 
  distinct(lobster_strata, area_km2) %>% 
  ggplot(aes(x = area_km2, fct_reorder(lobster_strata, as.numeric(area_km2)), fill = lobster_strata)) +
  geom_col() +
  scale_x_continuous(labels = comma_format()) +
  labs(y = "Lobster Strata", x = "Area (km^2)", fill = "Lobster Strata")
```


### Estimate Area-Stratified Catch

Area-stratified catch estimates are an approach that uses strata specific catch rates which are weighted by their overall size.

**Area Stratification Function:**

```{r}
stratify_lobster_strata_catch <- function(survdat_weights, area_label, area_col){
  
  # https://noaa-edab.github.io/survdat/articles/calc_strat_mean.html
  
 # # Testing:
 #  area_label <- "lobster_strata"
 #  area_col <- "area_km2"
 
  # column symbols from strings
  label_sym <- sym(area_label)
  areas_sym <- sym(area_col)
  
  ####  1. Set Constants: 
  # Area covered by an albatross standard tow in km2
  alb_tow_km2 <- 0.0384
  # catchability coefficient - ideally should change for species guilds
  q <- 1
  
  
  ####  2. Stratum Area & Effort Ratios 
  # Get Annual Stratum Effort, and Area Ratios
  # The number of tows in each stratum by year
  # area of a stratum relative to total area of all stratum sampled that year
  
  # Get Total area of all strata sampled in each year
  total_stratum_areas <- group_by(survdat_weights, est_year)
  total_stratum_areas <- distinct(total_stratum_areas, {{label_sym}}, .keep_all = T)
  total_stratum_areas <- summarise(total_stratum_areas,
                                   tot_s_area =  sum({{areas_sym}}, na.rm = T),
                                   .groups = "drop")
  
  
  # Calculate strata area relative to total area i.e. stratio or stratum weights
  survdat_weights <- left_join(survdat_weights, total_stratum_areas, by = "est_year")
  survdat_weights <- mutate(survdat_weights, 
                                   st_ratio = {{areas_sym}} / tot_s_area,
                                   st_ratio = as.numeric(st_ratio))
  
  
  # We have total areas, now we want effort within each
  # Number of unique tows per stratum, within each season
  yr_strat_effort <- group_by(survdat_weights, est_year, season, {{label_sym}})
  yr_strat_effort <- summarise(yr_strat_effort, strat_ntows = n_distinct(id), .groups = "drop")
  
  # Add those yearly effort counts back for later
  # (area stratified abundance)
  survdat_weights <- left_join(survdat_weights, yr_strat_effort, 
                               by = c("est_year", "season", area_label))
  
  ####  4. Derived Stratum Area Estimates
  
  ## A. Catch per tow
  survdat_weights <- survdat_weights %>% 
    mutate(
      # Length Based:
      # Catch / tow, for that year & season group
      abund_tow_s   = numlen_adj / strat_ntows,
      # length based: biomass / tow
      lwbio_tow_s = sum_weight_kg / strat_ntows,
      
      # Not Length Based: 
      # Aggregate biomass is repeated across length classes for each station for each species
      # the number of length classes is tallied in the cleanup code-
      # where the conversion factor is done
      biom_per_lclass = (biomass_kg / n_len_class),
      biom_tow_s = biom_per_lclass / strat_ntows)
      
  
  ## B. Stratified Mean Catch Rates 
  # (catch rate, weighted by relative size of stratum)
  # stratum area : area of all stratum sampled that season
  survdat_weights <-  survdat_weights %>% 
    mutate(
      # Length Based:
      # Stratified mean abundance CPUE
      strat_mean_abund_s = abund_tow_s * st_ratio,
      # Stratified mean LW Biomass
      strat_mean_lwbio_s = lwbio_tow_s * st_ratio,
      
      # Not length based:
      # Stratified mean BIOMASS CPUE
      strat_mean_biom_s = biom_tow_s * st_ratio)
  
  
  ## C. Stratified Total Abundance/Biomass
  # convert from catch rate by area swept to total catch for entire stratum
  survdat_weights <-  survdat_weights %>% 
    mutate(
      # Length Based:
      # Total Abundance
      strat_total_abund_s = round((strat_mean_abund_s * tot_s_area / alb_tow_km2) / q),
    
      # Two options for to estimate lw biomass
      # Result is the same 4/20/2021
      # Option 1: Individual LW Biomass * expanded abundance at length
      strat_total_lwbio_s = (ind_weight_kg * strat_total_abund_s) / q,
      # # Option 2: Size specific lw biomass / tow, expanded to total area
      # strat_total_lwbio_s  = (strat_mean_lwbio_s * tot_s_area / alb_tow_km2) / q
      
      # Not Length Based:
      # Total BIOMASS from the biomass of all lengths
      strat_total_biom_s = (strat_mean_biom_s * tot_s_area / alb_tow_km2) / q)
  
  
  
  ## D. abundance/biomass per km instead of relative weights?
  
}

```


**Run Stratification:**

```{r}
# Run stratification
gom_strat <- stratify_lobster_strata_catch(survdat_weights = gom_weights, 
                                           area_label = "lobster_strata", 
                                           area_col = "area_km2")


# Tidy up?
# there are now two different "stratum columns" floating around
gom_strat <- gom_strat %>% 
  select(-c(strat_num, stratum, nafodiv, full_name, 
            st_ratio, strat_ntows, biom_per_lclass)) 

```


### Pull Predator Complex

The last step before estimating any of the indices is to pull out the species that prey on lobster

```{r}
lobster_predators <- c(
  "atlantic halibut",
  "atlantic wolffish",
  "barndoor skate",
  "black sea bass",
  "atlantic cod",
  "fourspot flounder",
  "haddock",
  "little skate",
  "longhorn sculpin",
  "ocean pout",
  "red hake",
  "sea raven",
  "silver hake",
  "smooth skate",
  "spiny dogfish",
  "spotted hake",
  "thorny skate",
  "white hake",
  "winter flounder"
)


# Filter
gom_predators <- gom_strat %>% 
  filter(comname %in% lobster_predators) %>% 
  mutate(lobster_pred = "lobster predator")
```


## Summarize Predator Patterns

Depending on whether we are looking at metrics on individuals (bodysize) or across individuals (total fishes, total biomasses) there is a need to either weight/un-weight the averaging for these summaries.


```{r}
# get stratified mean abundances
predator_summs <- gom_predators %>% 
  bind_rows(gom_predators %>% mutate(season = "Both")) %>% 
  group_by(est_year, season, lobster_strata, lobster_pred) %>% 
  summarise(
    # station details
    `station total` = n_distinct(id),
    # Survey totals
    `total fish` = sum(numlen_adj),
    `total biomass (kg)` = sum(sum_weight_kg),
    
    # Survey Means
    `average abundance` = mean(numlen_adj),
    `mean weight (kg)` = weighted.mean(ind_weight_kg, numlen_adj),
    `mean length (cm)` = weighted.mean(length_cm, numlen_adj),
    #  Stratified Means
    # Should these averages be weighted by the number of fish caught?
    `stratified mean abundance` = mean(strat_mean_abund_s),
    `stratified mean biomass (kg)` = mean(strat_mean_lwbio_s),
    `strat-abund weighted mean abundance` = weighted.mean(strat_mean_abund_s, strat_total_abund_s),
    `strat-abund weighted mean biomass (kg)` = weighted.mean(strat_mean_lwbio_s, strat_total_abund_s),
    # Average Sizes
    
    `stratified mean length (cm)` = weighted.mean(length_cm, strat_total_abund_s),
    
    `stratified mean weight (kg)` = weighted.mean(ind_weight_kg, strat_total_abund_s),
    # Stratified Totals
    `stratified total abundance` = sum(strat_total_abund_s),
    `stratified total biomass (kg)` = sum(strat_total_lwbio_s),
            .groups = "drop") %>% 
  mutate(season = factor(season, levels = c("Spring", "Fall", "Both")))

```


## Assess Predator Indices {.tabset .tabset-pills}

To look at metrics over time we can plot each season or the aggregate of both against one another:

**Plotting Function:**

```{r}
# Stop re-typing code
plot_pred_index <- function(pred_dat, col_select = "stratified total biomass (kg)"){
  col_sym <- sym(col_select)
  ggplot(pred_dat, aes(x = est_year, y = {{col_sym}}, color = season)) +
    geom_line(alpha = 0.2) +
    geom_point(alpha = 0.6, size = 1) +
    geom_smooth(formula = y~x, method = "loess") + 
    scale_color_gmri() +
    facet_grid(lobster_strata~season, scales = "free") + 
    scale_y_continuous(labels = scales::comma_format()) +
    labs(x = "", y = str_replace_all(col_select, "_", " "),
         subtitle = str_c("Lobster Predator Complex: \n", str_to_title(col_select))) +
    theme(legend.position = "right",
          axis.text.x = element_text(angle = 45, hjust = 1)) +
    guides(color = guide_legend(title = "Season", title.position = "top", title.hjust = 0.5))
  
}
```




### Abundance {.tabset}

#### Observed

```{r}
plot_pred_index(predator_summs, col_select = "total fish")
```

#### Stratified

```{r}
plot_pred_index(predator_summs, col_select = "stratified total abundance")
```

### Biomass {.tabset}

#### Observed

```{r}
plot_pred_index(predator_summs, col_select = "total biomass (kg)")
```

#### Stratified

```{r}
plot_pred_index(predator_summs, col_select = "stratified total biomass (kg)")
```

### Length {.tabset}

#### Observed

```{r}
plot_pred_index(predator_summs, col_select = "mean length (cm)")
```

#### Stratified

```{r}
plot_pred_index(predator_summs, col_select = "stratified mean length (cm)")
```

### Weight {.tabset}

#### Observed

```{r}
plot_pred_index(predator_summs, col_select = "mean weight (kg)")
```

#### Stratified

```{r}
plot_pred_index(predator_summs, col_select = "stratified mean weight (kg)")
```




`r insert_gmri_footer()`


